TESSELLATE asteroids paper

### 2025-09-04 PaperDraft/paperDraft.tex
some numbers added

\red{A Number \#\#\#} of asteroids with $V\leq \qty{20}{\mag}$ were found in the sectors we analysed.
Most of these are too faint for the lightcurve to give a reliable and period.
Once the quality checks described above have been applied, we are left with \red{A smaller number \#\#\#} of planetesimals with accurate rotation rates.
\red{Some fraction} of these asteroids are not in the LCDB,%TODO check defind before
so we are the first to get the rotation period for these bodies.

>>>>

\red{57426} of asteroids with $V\leq \qty{20}{\mag}$ were found in the year 3 sectors we analysed.
Most of these are too faint for the lightcurve to give a reliable and period, while \citet{Pal2018} thinks good photometry down to $V\lesssim \qty{19}{\mag}$ should be achievable, we find the limit for \tessellate\ is closer to $m_{T} \approx \qty{17}{\mag}$ \citepalias{TESSELLATE}.
Once the quality checks (described above) have been applied, we are left with \red{4328} of planetesimals with accurate rotation rates.
\red{Some fraction} of these asteroids are not in the LCDB,%TODO check defind before
so we are the first to get the rotation period for these bodies.
